High Resolution Identification of Protein-DNA Binding Events and Quality Control for ChIP-exo data

### 2015-11-10 rmarkdown/chip_exo_paper.Rnw
Finished analysis of local SCC for Sig70 data

\begin{figure}[h]
  \centering

  \caption{This is a place-holder figure by now. The idea of this segments it }
  \label{fig:fsr}
\end{figure}

@@

We compared

>>>>

% \begin{figure}[h]
%   \centering

%   \caption{This is a place-holder figure by now. The idea of this segments it }
%   \label{fig:fsr}
% \end{figure}

@@

<<comp_param,include = FALSE,echo = FALSE,eval = TRUE>>=

  bin_size <- 150
  frag_len <- 150

We first compared various factors that could affect binding site
identification between ChIP-exo and ChIP-Seq data. in order to compare
distribution of signal and background between ChIP-exo and ChIP-Seq
data, we calculated ChIP tag counts accross the genome by counting the
number of reads mapping to each of \Sexpr{bin_size} non-overlapping
window after extending reads by \Sexpr{frag_len} to their 3' end
directions. ChIP tag counts in ChIP-exo data were linearly related to
ChIP tag counts in ChIP-Seq data for the regions with high ChIP tag
counts (Figure \ref{fig:comp}A). This implies that signals for
pontential binding sites are well reproducible between ChIP-exo and
ChIP-Seq data. On the other hand, there was clear difference in the
background distribution between them. In CHIP-Seq datam reads were
almost uniformly distributed over background (non-binding) regions and
the ChIP tag counts in there regions were significantly larger than
zero. In contrast, in ChIP-exo data, there was larger variation in
ChIP tag counts among background regions and ChIP tag counts were much
lower in these regions compared to ChIP-Seq data. There were also
large proportion of regions without any read in ChIP-exo data. There
results indicate that background distribution of CHIP-exo data is less
homogeneous than that of ChIP-Seq data.

### 2015-11-10 rmarkdown/chip_exo_paper.tex
Finished analysis of local SCC for Sig70 data

We compared

>>>>

We first compared various factors that could affect binding site
identification between ChIP-exo and ChIP-Seq data. in order to compare
distribution of signal and background between ChIP-exo and ChIP-Seq
data, we calculated ChIP tag counts accross the genome by counting the
number of reads mapping to each of 150 non-overlapping
window after extending reads by 150 to their 3' end
directions. ChIP tag counts in ChIP-exo data were linearly related to
ChIP tag counts in ChIP-Seq data for the regions with high ChIP tag
counts (Figure \ref{fig:comp}A). This implies that signals for
pontential binding sites are well reproducible between ChIP-exo and
ChIP-Seq data. On the other hand, there was clear difference in the
background distribution between them. In CHIP-Seq datam reads were
almost uniformly distributed over background (non-binding) regions and
the ChIP tag counts in there regions were significantly larger than
zero. In contrast, in ChIP-exo data, there was larger variation in
ChIP tag counts among background regions and ChIP tag counts were much
lower in these regions compared to ChIP-Seq data. There were also
large proportion of regions without any read in ChIP-exo data. There
results indicate that background distribution of CHIP-exo data is less
homogeneous than that of ChIP-Seq data.
